Molecular dynamics simulation of synchronization in driven particles

### 2021-01-26 manuscript/manuscript_ajp_2020.tex
slight text edits including abstract

\begin{abstract}
  Synchronization
  plays a key role in many physical processes.
  %Simplified models
  %such as 
  %What problem did you study and why is it important?
  Modeling synchronization
  with simulations and table-top experiments
  can 
  provide insight
  to complex behaviors
  in the natural world.
  Driving particles
  across a washboard potential energy landscape
  is a 
  common 
  technique to isolate complex 
  synchronized patterns 
  in both simulations and experiments.
  %as observed in 
  %experiments %al systems 
  %of %interest to condensed matter physics %including 
  %magnetically driven colloidal particles
  %confined by light-fields.
  %exhibit a variety of synchronization effects.
  %in
  %  Numerical model
  We discuss a simple
  numerical model %that
  %exhibits
  %provides insight
  %to synchronization behavior
  %and
  %atoms on surfaces.
  %voltage driven superconducting vortices
  %confined in a Josephson junction,
  %and ac and dc driven
  %charge and spin density waves.
  %We present the basics
  using
  molecular dynamics simulations
  for particles moving through
  a viscous liquid.
  %
  %applied to single and multiple particle systems.
  %so we model the dynamics of each particle
  %with 
  %overdamped equations of motion.
  Our results show a variety of synchronization effects 
  in single and multi-particle systems, 
  %and detect synchronization using
  %measurements of
  which we characterize with
  plots of 
  particle velocity as a function of applied driving force,
  and phase diagrams of position versus velocity.
  %We demonstrate how to 
  %visualize
  %the system with
  %numerical representations of the landscape
  %and
  %animations of the particle motion.
  %We include sample code
  %and exercises for students
  %with 
  %opportunities
  %to reproduce our results and propose
  %new numerical experiments.
  %With only a few particles in two-dimensions,
  %the simulation runs quickly,
  %making this an appropriate model for undergraduates to explore.  
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

@@

%Given the prevalence of synchronization,
%it is the subject of many computational models.
Here we perform numerical studies 
on the synchronized dynamics
of confined particles driven over
a washboard shaped potential energy landscape.
%Numerical studies %of harmonic systems
%can yield insights
%to the mechanics of naturally oscillating systems.
We chose this model for its
relevance to condensed matter systems
and ease of simulation.
%---------------------------------------------------------------
%kinks and nanofriction
%-----------------------------------------------------------------
%transition from synchronized to chaotic
%describe types of physical systems - particle types
%%In this work,
%we perform 
%numerical simulations of confined, driven particles
%to model a variety of physical phenomena.
%-----------------------------------------------------------------------
%paper outline
%In the following paper
%In Section~\ref{sec:colloids} we describe colloid particles,
%an relevant
%experimental analog of our simulations.
We describe
our molecular dynamics model for a single particle in Section~\ref{sec:MD}.
%In this section, we restrict our discussion to a single particle,
%and include additional information
%for multiple particles in Section~\ref{sec:sync}.
%including various  and confining environments.
We summarize
our results 
%in Section~\ref{sec:results} 
including synchronized motion of a single confined particle
driven across a periodic landscape in 
Section~\ref{sec:one}.
%In Section~\ref{sec:sync}
%we 
%extend the model to include multiple particles,
%and show how confined 
%interacting particles respond to the same applied driving force.
%including stationary propagation of high density kinks
%in Sec.~\ref{sec:kink}.
%We include code to simulate
%and visualize the landscape and dynamics in this section
%and supplementary material.
%we
%demonstrate how uniform environments and applied forces
%and create synchronized flow patterns.
%We present these results using standard tools of non-linear oscillators
%such phase diagrams of velocity versus position.
%PHASE DIAGRAMS SHOWING COUPLING, OR QUASI-PERIODIC COUPLING
%INDICATE COOPERATIVE MOTION IN THE Q1D SUBSTRATE
%In Section~\ref{sec:quasiperiod},
%we show how an aperiodic landscape modifies the particle dynamics.
%Finally we explore the transition to chaotic dynamics in 
%Section~\ref{sec:chaos}
%and conclude 
We conclude with
exercises for interested students 
in Section~\ref{sec:problems}.
In Section~\ref{sec:conclusion}
we describe how our work with colloids applies more broadly
to many physical systems
such as dusty plasmas, superconducting vortices and Josephson junctions.

@@

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{landscape.pdf}
\caption{
  Schematic of the simulation
  of a single particle
  driven across a washboard potential
  energy landscape.
  The period of the landscape is $\lambda = L/N_p$,  
  %is marked in red,
  where $N_p = 3$.  
  The force due to the landscape %$\vec{F}^l$
  is calculated from the gradient of the potential
  energy 
  $\vec{F}^l = -\nabla U(\vec{r})$.
  (a) View of the $x-y$ plane. %of the simulation
  The time-dependent applied driving force $\vec{F}^d$
  is parallel to the y-axis.
  The landscape is shown with a contour plot,
  with maxima in the potential energy marked in red
  and minima marked in blue.
  A particle is shown in the region between minima and maxima
  subject to competing forces of the landscape and applied driving force.
  (b) The potential energy function
  along the y-axis $U_l(y)$.  
  The particle in (a) is shown at the same $y-$position.
  The slope of $U_l(y)$ is the 
  magnitude of force $\vec{F}^l$. %is calculated
  %as the slope of this function,
  %directed along the $y-$direction in panel (a).
  }
\label{fig:landscape0}
\end{figure}
\end{center}

@@

%because
The inertia of 
small particles is reduced by interactions
with fluid particles \cite{Purcell1977}.
In this model 
colloids are overdamped
-- i.e. suspended in a continuous viscous fluid
that dissipates energy %at a rate
such 
that the particles do not accelerate.
%that greatly impedes their motions.
Energy dissipation from the fluid is modeled
with a frictional force on particle with velocity $\vec{v}_i$
%that removes energy from
%the particles,
%which we model as
$\vec{F}^{drag}_i = -\eta \vec{v}_i$
%proportional to the particle velocity 
with a friction coefficient $\eta$
proportional to the fluid viscosity.
We discuss friction models for
spheres moving through fluids in 
%Section~\ref{sec:problems}
Exercise~\ref{ex:reynolds}. %for more information
%We model the particle dynamics  with an overdamped equation of motion. Models with inertia set to zero are appropriate for moving through a high viscosity fluid
Newton's second law for an individual particle
%$m \vec{a}_i = \sum \vec{F}$
is simplified
by the assumption $\vec{a}_i$ is zero. % in the overdamped model.
%Newton's second law can be rearranged %for the velocity
%to
The overdamped equation of motion for an isolated particle is
%solved for velocity 
\begin{equation}
  \eta \vec{v}_i = \vec{F}^l_{i}(\vec{r}_i) + \vec{F}^{d}(t).
    \label{eq:motion}
\end{equation}
with  $\eta = 1$.  
%which we describe in more detail in Table~\ref{tab:1}
%and Exercise~\ref{ex:reynolds}.
%In %Section~\ref{sec:problems}
%Exercise~\ref{ex:n2l}
%we invite the reader to confirm this result.
The equation of motion provides a direct calculation of the velocity
of an individual particle from its location $\vec{r}_i$ %in the simulation
and the simulation time.

The molecular dynamics simulation is controlled by a $for()$ loop
which runs from an initial to maximum integer number of time steps.
%$t_i$.
Each integer time step interval %$t_{i+1}-t_i$
represents a simulation time interval of $\Delta t$ 
simulation units.  %as described in Table 1
At each time step
we evaluate the net force on each particle as a function of its position
$\vec{r}_i(t)$
and then integrate
the equation of motion to move particles
to an updated position.
%$\vec{r}_i(t+\Delta t)$.%
Since the acceleration as zero,
the integration of the equation of motion
is performed via 
the Euler method 
\begin{equation}
  \vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t)
    \label{eq:euler}
\end{equation}
for a small time step $\Delta t = 0.001 \tau$.
In %Section~\ref{sec:problems}
Exercise~\ref{ex:euler}
we describe 
the numerical methods for 
solving differential equations.
%
The units of the simulated variables are summarized in Table ~\ref{tab:1}.

\begin{table}[h!]
\centering
\caption{Simulation units and comparable
  experimental values~\cite{Juniper2015}.}
%{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
\begin{ruledtabular}
\begin{tabular}{c c c } %p{5cm}}
Quantity & Simulation Unit & Experimental range\\
\hline
length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
energy & $E_0 = 1$ & $ < E_0 <$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
%dimensionless interaction strength & $q$ \\
%effective colloidal charge & $Z^*$ \\
%solvent dielectric constant & $\epsilon \epsilon_0$\\
force & $F_0 = E_0 / a_0$ & $<F_0<$\\
velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $ <\eta<$\\
%juniper uses water–ethanol mixture
time &  $ \tau = \eta a_0 / F_0 $ & $ < \tau <$\\
period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
potential amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
temperature & $T_0 = 0$ \footnote{a. see Ex.~\ref{ex:brownian} to include temperature.} & $T \sim 300K $ \\

@@

The competition between the driving force and landscape potential
can produce a variety of hopping patterns in the particle motion. 
%In Fig.~\ref{fig:0}
%reaching a minimum position
%of $y/\lambda = 1$
%over the total period $T = 100$.
%In Fig. ~\ref{fig:0}
%the average displacement during one time period is a single wavelength
%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
%single dc case with figure
%dc_current 0.01
%ac_current 0.05
%ac_frequency 0.01
%fp_y 0.1
%
The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
control the rate and distance a  particle moves 
forward and backward in the landscape.
To explore the possible hopping patterns,
we sweep through a range of $F^{dc}$ for fixed $F^{ac}$ and $A_p$
to illustrate
distinct oscillation modes as a function of $F^{dc}$.
A mode is a periodic pattern of hops
with a constant average particle velocity, $\langle {v}_{y} \rangle$
over a range of driving forces $F^{dc}$.
%as shown
In Fig.~\ref{fig:1} 
we keep $F^{dc}$ constant
for $10^5$ simulation timesteps
and 
measure the average velocity $\langle v_y \rangle $ 
as a function of $F^{dc}$,
with $F^{ac} = 0.05$, $f=0.01$, and the landscape %force $\vec{F}^{l}$
shown in Fig.~\ref{fig:0}.
%We plot the results in Fig.~\ref{fig:1} for 
The modes appear as 
discrete steps in $\langle v_y \rangle$ %occur because
across a range of $F^{dc}$,

@@

  To first order 
  approximate experimental values for
  a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
  Viscosity of water decreases with temperature
  from $1.3 \times 10^{-3}$ Pa-s at $10^{\circ}$ C to 
  from $0.31 \times 10^{-3}$ Pa-s at $90^{\circ}$ C,
  making $\eta \sim 10^{-3}$ Pa-s,
  where 1 Pascal is $1$ N/m$^2$.
  Likewise the density $\rho$ varies with temperature
  but  $\rho \sim 10^3$ kg/cm$^3$ is a reasonable
  first order approximation.
  \cite{asce}

@@

@@

@@

\section{Conclusion}
\label{sec:conclusion}	% You can label sections for reference
A single particle oscillator
in a potential well is 
much like a skateboarder in a half-pipe or
a child on a swing.
If subject to an applied force,
a confined oscillator may 
synchronize its location
to the periodic pattern of the external drive,
moving back and forth in time with
the beat. 
%Fundamental models
%of synchronization 
%can %include many coupled oscillators
%or
%focus on
We have used 
a single particle driven across a periodic potential landscape 
%Single particle studies are useful
to study synchronization dynamics. 
%due to interactions between particles.
The relationship between the driving force and
landscape can change the pattern of motion.  
With a constant or 
dc drive the landscape modulates 
the particle velocity, below some threshold  
the dc force is not strong enough to push the particle
across a potential maximum so the average velocity is zero,
a phenomena referred to as pinning \cite{Reichhardt2017}.  
%and dissipating energy from the system at all driving forces.
A sinusoidal or ac drive creates mode-locking,
where the average particle velocity
is fixed for a range of dc drive forces \cite{Reichhardt2015}.

Our simulations reproduce results presented in 
Juniper {\it et al.} \cite{Juniper2015, Juniper2018}
which demonstrated
mode locking in
experiments and simulations of 
driven colloids on a
optical periodic landscape.
Due to the relative ease of
manipulation and imagining, 
colloids are used as experimental models
for systems relatively hard to access and visualize. 
Collections of colloids can
be used to study the properties of solids and liquids
%comprised of smaller particles
%such as atoms \cite{} or electrons \cite{}
or more exotic systems 
such as cold atoms or electron gases \cite{Grier2003}.
%Oscillators ordered into chains or lattices.
%has many important
%technological applications
Dynamical mode-locking
is %often
observed
in quantum electronic
devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
A single junction contains 
two superconductoring layers which sandwich an insulating layer.
When subject to an external voltage,
Cooper pairs in the superconducting materials
tunnel through the insulating layer.
Phase-locking is observed as 
%phase-locked current loops \cite{} 
stepped regions in current-voltage (I-V) relationship in these devices,
where voltage is the analog of external driving force
and current is that of particle velocity.
%where a constant current results from a range of voltages
%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
%instead of ohmic relationships.
Known as Shapiro steps, % \cite{},
these phase locked currents  
have been observed due to applied ac voltages in 
single Josephson junctions \cite{Shapiro1963, Golubov2004} and
coupled arrays of junctions \cite{Benz1990}.
%either in 
%velocity-force curves and voltage-current curves \cite{Golubov2004}.
Shapiro steps vary in width depending on the strength of the
applied ac forces,
and are observed in a variety of systems
displaying
%are hallmarks of
non-Ohmic behavior in voltage-current curves,
including
ac and dc driven
charge and spin density waves
and superconducting vortices in landscapes 
engineered with periodic patterns of pinning sites.
Thus the study of
mode-locking is a useful problem
of complex quantum mechanical systems.
Our results can be relevant 
to synchronization effects
in a broad range of experiments systems
including optically confined colloids,
superconductors with periodic pinning arrays, 
and the charge and spin of atomic systems.

>>>>

\begin{abstract}
  Synchronization
  plays a key role in many physical processes.
  We discuss a simple
  numerical model %that
  of synchronized particles 
  %exhibits
  %provides insight
  %to synchronization behavior
  %and
  %atoms on surfaces.
  %voltage driven superconducting vortices
  %confined in a Josephson junction,
  %and ac and dc driven
  %charge and spin density waves.
  %We present the basics
  using
  molecular dynamics simulations
  for particles moving through
  a viscous liquid.
  %Simplified models
  %such as 
  %What problem did you study and why is it important?
  Modeling synchronization
  with simulations and table-top experiments
  can 
  provide insight
  to complex behaviors
  in the natural world.
  We drive 
  particles
  across a washboard potential energy landscape, 
  a 
  common 
  technique to isolate complex 
  synchronized patterns 
  in both simulations and experiments.
  %as observed in 
  %experiments %al systems 
  %of %interest to condensed matter physics %including 
  %magnetically driven colloidal particles
  %confined by light-fields.
  %exhibit a variety of synchronization effects.
  %in
  %  Numerical model
  %
  %applied to single and multiple particle systems.
  %so we model the dynamics of each particle
  %with 
  %overdamped equations of motion.
  Our results show a variety of synchronization effects 
  in single and multi-particle systems, 
  %and detect synchronization using
  %measurements of
  which we characterize with
  plots of 
  particle velocity as a function of applied driving force,
  and phase diagrams of position versus velocity.
  %We demonstrate how to 
  %visualize
  %the system with
  %numerical representations of the landscape
  %and
  %animations of the particle motion.
  %We include sample code
  %and exercises for students
  %with 
  %opportunities
  %to reproduce our results and propose
  %new numerical experiments.
  %With only a few particles in two-dimensions,
  %the simulation runs quickly,
  %making this an appropriate model for undergraduates to explore.  
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

@@

%Given the prevalence of synchronization,
%it is the subject of many computational models.
Here we perform numerical studies 
on the synchronized dynamics
of confined particles driven over
a washboard shaped potential energy landscape.
%Numerical studies %of harmonic systems
%can yield insights
%to the mechanics of naturally oscillating systems.
We chose this model for its
relevance to condensed matter systems
and ease of simulation.
%---------------------------------------------------------------
%kinks and nanofriction
%-----------------------------------------------------------------
%transition from synchronized to chaotic
%describe types of physical systems - particle types
%%In this work,
%we perform 
%numerical simulations of confined, driven particles
%to model a variety of physical phenomena.
%-----------------------------------------------------------------------
%paper outline
%In the following paper
%In Section~\ref{sec:colloids} we describe colloid particles,
%an relevant
%experimental analog of our simulations.
We describe
our molecular dynamics model for a single particle in Section~\ref{sec:MD}.
%In this section, we restrict our discussion to a single particle,
%and include additional information
%for multiple particles in Section~\ref{sec:sync}.
%including various  and confining environments.
We summarize
our results 
%in Section~\ref{sec:results} 
including synchronized motion of a single confined particle
driven across a periodic landscape in 
Section~\ref{sec:one}.
%In Section~\ref{sec:sync}
%we 
%extend the model to include multiple particles,
%and show how confined 
%interacting particles respond to the same applied driving force.
%including stationary propagation of high density kinks
%in Sec.~\ref{sec:kink}.
%We include code to simulate
%and visualize the landscape and dynamics in this section
%and supplementary material.
%we
%demonstrate how uniform environments and applied forces
%and create synchronized flow patterns.
%We present these results using standard tools of non-linear oscillators
%such phase diagrams of velocity versus position.
%PHASE DIAGRAMS SHOWING COUPLING, OR QUASI-PERIODIC COUPLING
%INDICATE COOPERATIVE MOTION IN THE Q1D SUBSTRATE
%In Section~\ref{sec:quasiperiod},
%we show how an aperiodic landscape modifies the particle dynamics.
%Finally we explore the transition to chaotic dynamics in 
%Section~\ref{sec:chaos}
%and conclude 
We include 
exercises for interested students 
in Section~\ref{sec:problems}.
In Section~\ref{sec:conclusion}
we describe how our work with colloids applies more broadly
to many physical systems
such as dusty plasmas, superconducting vortices and Josephson junctions.

@@

@@

%because
The inertia of 
small particles is reduced by interactions
with fluid particles \cite{Purcell1977}.
In our model
we assume 
colloids are overdamped
-- i.e. colloids are suspended in a continuous viscous fluid
that dissipates energy %at a rate
such 
that the particles do not accelerate.
%that greatly impedes their motions.
Energy dissipation from the fluid is modeled
with a frictional force on particle with velocity $\vec{v}_i$ as
%that removes energy from
%the particles,
%which we model as
$\vec{F}^{drag}_i = -\eta \vec{v}_i$
%proportional to the particle velocity 
with a friction coefficient $\eta$
proportional to the fluid viscosity.
We discuss friction models for
spheres moving through fluids in 
%Section~\ref{sec:problems}
Exercise~\ref{ex:reynolds}. %for more information
%We model the particle dynamics  with an overdamped equation of motion. Models with inertia set to zero are appropriate for moving through a high viscosity fluid
\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{landscape.pdf}
\caption{
  Schematic of the simulation
  of a single particle
  driven across a washboard potential
  energy landscape.
  The period of the landscape is $\lambda = L/N_p$,  
  %is marked in red,
  where $N_p = 3$.  
  The force due to the landscape %$\vec{F}^l$
  is calculated from the gradient of the potential
  energy 
  $\vec{F}^l = -\nabla U(\vec{r})$.
  (a) View of the $x-y$ plane. %of the simulation
  The time-dependent applied driving force $\vec{F}^d$
  is parallel to the y-axis.
  The landscape is shown with a contour plot,
  with maxima in the potential energy marked in red
  and minima marked in blue.
  A particle is shown in the region between minima and maxima
  subject to competing forces of the landscape and applied driving force.
  (b) The potential energy function
  along the y-axis $U_l(y)$.  
  The particle in (a) is shown at the same $y-$position.
  The slope of $U_l(y)$ is the 
  magnitude of force $\vec{F}^l$. %is calculated
  %as the slope of this function,
  %directed along the $y-$direction in panel (a).
  }
\label{fig:landscape0}
\end{figure}
\end{center}
Newton's second law for an individual particle
%$m \vec{a}_i = \sum \vec{F}$
is simplified
by the assumption $\vec{a}_i$ is zero. % in the overdamped model.
%Newton's second law can be rearranged %for the velocity
%to
The overdamped equation of motion for an isolated particle is
%solved for velocity 
\begin{equation}
  \eta \vec{v}_i = \vec{F}^l_{i}(\vec{r}_i) + \vec{F}^{d}(t).
    \label{eq:motion}
\end{equation}
with  $\eta = 1$ in units of $v_0 / F_0$. 
%(see Table~\ref{tab:1}).
%and Exercise~\ref{ex:reynolds}.
%In %Section~\ref{sec:problems}
%Exercise~\ref{ex:n2l}
%we invite the reader to confirm this result.
The equation of motion provides a direct calculation of the velocity
of an individual particle from its location $\vec{r}_i$ %in the simulation
and the simulation time.

The molecular dynamics simulation is controlled by a $for()$ loop
which runs from an initial to maximum integer number of time steps.
%$t_i$.
Each integer time step interval %$t_{i+1}-t_i$
represents a simulation time of $\Delta t$ 
simulation units $\tau$.  %as described in Table 1
At each time step
we evaluate the net force on each particle as a function of its position
$\vec{r}_i(t)$
and then integrate
the equation of motion to move particles
to an updated position.
%$\vec{r}_i(t+\Delta t)$.%
Since the acceleration as zero,
the integration of the equation of motion
is performed via 
the Euler method 
\begin{equation}
  \vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t)
    \label{eq:euler}
\end{equation}
for a small time step $\Delta t = 0.001 \tau$.
In %Section~\ref{sec:problems}
Exercise~\ref{ex:euler}
we describe 
the numerical methods for 
solving differential equations.
%
The units of the simulated variables are summarized in Table ~\ref{tab:1}.

\begin{table}[h!]
\centering
\caption{Simulation units and comparable
  experimental values~\cite{Juniper2015}.}
%{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
\begin{ruledtabular}
\begin{tabular}{c c c } %p{5cm}}
Quantity & Simulation Unit & Experimental range\\
\hline
length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
energy & $E_0 = 1$ & $ < E_0 <$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
%dimensionless interaction strength & $q$ \\
%effective colloidal charge & $Z^*$ \\
%solvent dielectric constant & $\epsilon \epsilon_0$\\
force & $F_0 = E_0 / a_0$ & $<F_0<$\\
velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $\eta \sim 10^{-3}$ Pa-s \\
%juniper uses water–ethanol mixture
time &  $ \tau = \eta a_0 / F_0 $ & $ < \tau <$\\
period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
potential amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
temperature & $T_0 = 0$ \footnote{a. see Ex.~\ref{ex:brownian} to include temperature.} & $T \sim 300K $ \\

@@

The competition between the driving force and landscape potential
can produce a variety of hopping patterns in the particle motion. 
%In Fig.~\ref{fig:0}
%reaching a minimum position
%of $y/\lambda = 1$
%over the total period $T = 100$.
%In Fig. ~\ref{fig:0}
%the average displacement during one time period is a single wavelength
%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
%single dc case with figure
%dc_current 0.01
%ac_current 0.05
%ac_frequency 0.01
%fp_y 0.1
%
The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
control the rate and distance a  particle moves 
forward and backward in the landscape.
To explore the possible hopping patterns,
we sweep through a range of $F^{dc}$ for fixed $F^{ac}$ and $A_p$
to illustrate
distinct oscillation modes. % as a function of $F^{dc}$.
A mode is a periodic pattern of hops
with a constant average particle velocity, $\langle {v}_{y} \rangle$
over a range of driving forces $F^{dc}$.
%as shown
In Fig.~\ref{fig:1} 
we keep $F^{dc}$ constant
for $10^5$ simulation timesteps
and 
measure the average velocity $\langle v_y \rangle $ 
as a function of $F^{dc}$,
with $F^{ac} = 0.05$, $f=0.01$, and the landscape %force $\vec{F}^{l}$
shown in Fig.~\ref{fig:0}.
%We plot the results in Fig.~\ref{fig:1} for 
The modes appear as 
discrete steps in $\langle v_y \rangle$ %occur because
across a range of $F^{dc}$,

@@

  To first order 
  approximate experimental values for
  a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
  %Likewise
  To first order $\eta \sim 10^{-3}$ Pa-s 
  since 
  viscosity of water decreases with temperature
  from $1.3 \times 10^{-3}$ Pa-s at $10^{\circ}$ C to 
  from $0.31 \times 10^{-3}$ Pa-s at $90^{\circ}$ C,
  where 1 Pascal is $1$ N/m$^2$.
  Likewise the liquid density $\rho$ varies with temperature
  but  $\rho \sim 10^3$ kg/cm$^3$ is a reasonable
  first order approximation
  \cite{asce}.

@@

  {\it small timesteps matter a great deal when particle interactions
    are included in the model.  I have demonstrated that
    without particle interactions we can increase the timestep
  with no penalty, so this isn't a very interesting problem.}

@@

  {\it I have python code that does all of this, but I don't have it
    set up to play nice with my new python MD code}

@@

\section{Conclusion}
\label{sec:conclusion}	% You can label sections for reference
A single particle oscillator
in a potential well is 
much like a skateboarder in a half-pipe or
a child on a swing.
If subject to an applied force,
a confined oscillator may 
synchronize its location
to the periodic pattern of the external drive,
moving back and forth in time with
the beat. 
%Fundamental models
%of synchronization 
%can %include many coupled oscillators
%or
%focus on
We have used 
a single particle driven across a periodic potential landscape 
%Single particle studies are useful
to study synchronization dynamics
that arise due to the interplay
between a particles environment and external forces.
%due to interactions between particles.
The relationship between the driving force and
landscape can change the pattern of motion.  
With a constant or 
dc drive the landscape modulates 
the particle velocity, below some threshold  
the dc force is not strong enough to push the particle
across a potential maximum so the average velocity is zero,
a phenomena referred to as pinning \cite{Reichhardt2017}.  
%and dissipating energy from the system at all driving forces.
A sinusoidal or ac drive creates mode-locking,
where the average particle velocity
is fixed for a range of dc drive forces \cite{Reichhardt2015}.

Our simulations reproduce results presented in 
Juniper {\it et al.} \cite{Juniper2015, Juniper2018}
which demonstrated
mode locking in
experiments and simulations of 
driven colloids on a
optical periodic landscape.
Due to the relative ease of
manipulation and imagining, 
colloids are used as experimental models
for systems relatively hard to access and visualize. 
Collections of colloids can
be used to study the properties of solids and liquids
%comprised of smaller particles
%such as atoms \cite{} or electrons \cite{}
or more exotic systems 
such as cold atoms or electron gases \cite{Grier2003}.
%Oscillators ordered into chains or lattices.
%has many important
%technological applications
Dynamical mode-locking, the primary synchronization
effect explored in this paper, 
is %often
observed
in quantum electronic
devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
A single junction contains 
two superconductoring layers which sandwich an insulating layer.
When subject to an external voltage,
Cooper pairs in the superconducting materials
tunnel through the insulating layer.
Phase-locking is observed as 
%phase-locked current loops \cite{} 
stepped regions in current-voltage (I-V) relationship in these devices,
where voltage is the analog of external driving force
and current is that of particle velocity.
%where a constant current results from a range of voltages
%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
%instead of ohmic relationships.
Known as Shapiro steps, % \cite{},
these phase locked currents  
have been observed due to applied ac voltages in 
single Josephson junctions \cite{Shapiro1963, Golubov2004} and
coupled arrays of junctions \cite{Benz1990}.
%either in 
%velocity-force curves and voltage-current curves \cite{Golubov2004}.
Shapiro steps vary in width depending on the strength of the
applied ac forces,
and are observed in a variety of systems
displaying
%are hallmarks of
non-Ohmic behavior in voltage-current curves,
including
ac and dc driven
charge and spin density waves
and superconducting vortices in landscapes 
engineered with periodic patterns of pinning sites.
Thus the study of
mode-locking is a useful problem
of complex quantum mechanical systems.
Our results can be relevant 
to synchronization effects
in a broad range of experiments systems
including optically confined colloids,
superconductors with periodic pinning arrays, 
and the charge and spin of atomic systems.
